Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-11-13 Writing/manuscript.tex
Updates from Overleaf

\begin{itemize}
\item
  start a discussion about the implications of the use of mis-measured water use for water use regulation.
\item
  shed lights on unintentional consequences of using estiamtes rather than actual measurements
\end{itemize}

@@

Figure \ref{fig:profit-quota-water-het} below compares profit from agricultural production as a function of actual water use between water and proxy quota across three different production heterogeneity levels and the size of the measurement errors. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use. However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota. It can be shown that water quota always outperforms proxy quota on average irrespective of the degere of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix). Not surprisingly, profit losses of using proxy quota increase as measurement error size increases. Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.

@@

We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota. Figure \ref{fig:illust-homegeneous} presents a case with two homegeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 29.9 less under the water quota system compared to the proxy quota system. However, Farmer A makes 128.9 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

>>>>

\begin{itemize}
\item
  start a discussion about the implications of the use of mis-measured water use for water use regulation.
\item
  shed light on unintentional consequences of using estimates rather than actual measurements.
\end{itemize}

@@

Figure \ref{fig:profit-quota-water-het} below compares the profit from agricultural production as a function of actual water use between the water and proxy quota at three different levels of production heterogeneity and the size of the measurement errors. When there is no heterogeneity in farmers' production function, water quota is the most cost effective way to achieve a water use reduction goal (highest profit achievable for a given level of actual water use). Under this circumstance, proxy quota with unbiased measurement errors achieves worse than water quota due to asymmetry in downside and upside risk of water use. However, as production heterogeneity increases, water quota loses its comparative advantage over proxy quota. It can be shown that water quota always outperforms proxy quota on average irrespective of the degree of production heterogeneity when measurement error is independent and production function is concave (show proof in appendix). Not surprisingly, profit losses of using proxy quota increase as measurement error size increases. Profit loss of using proxy-based quota tends to become greater as the toal realized water use becomes smaller.

@@

We now look at simple two-farm exams to build intuition behind the profit loss due to the use of proxy quota in place of water quota. Figure \ref{fig:illust-homegeneous} presents a case with two homogeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 29.9 less under the water quota system compared to the proxy quota system. However, Farmer A makes 128.9 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.
